---
title: "2-16 Clean Data for Visuals"
author: "Adam Sneath"
date: "February 14, 2019"
output: pdf_document
---

## Filter the data to individual .csv files for C12, C14, C15, C17, C20
### Use as a template for filtering to any specific measure(s)
### Note for Pitt students: All .csv files will be uploaded to the box folder "Data (see README)" for access on your own device or generally in R Studio 

### The measures are defined as follows: 

#### C12: Osteoporosis Management in Women Who Had a Fracture - The percentage of female Members age 67 - 85 who suffered a fracture and who had either a bone mineral density (BMD) test or prescription for a drug to treat or prevent osteoporosis in the six months after the fracture. 

#### C14: Comprehensive Diabetes Care: Medical Attention for Nephropathy (kidney damage) - The percentage of diabetic Members age 18 - 75 who had medical attention for nephropathy.

#### C15: Comprehensive Diabetes Care: HbA1c Control (<=9%) - The percentage of Members age 18 - 75 with diabetes (type 1 or type 2) whose most recent Hemoglobin A1C is <=9.0%. 

#### C17: Disease-Modifying Anti-Rheumatic Drug Therapy for Rheumatoid Arthritis - The percentage of Members age 18 and older who were diagnosed with rheumatoid arthritis and who were dispensed at least one ambulatory prescription for a disease-modifying anti-rheumatic drug (DMARD). 

#### C20: Medication Reconciliation Post-Discharge - The percentage of discharges from January 1-December 1 of the measurement year for Members 18 years of age and older for whom medications were reconciled the date of discharge through 30 days after discharge (31 total days). 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stringr)
library(sas7bdat)
library(ggplot2)
library(ggmap)
library(readxl)
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE)
setwd("C:/Users/adsne/Desktop/2019 Spring/Healthcare/Project")
prac <- read.csv("18-Feb-19_practice_geocoded.csv")
zip_inc <- read_excel("2006-2010_US_income_by_zip_UMICH.xlsx")
```

```{r Find Missing Zips}
setdiff(prac$Zip,zip_inc$Zip)
```

```{r Join Household Income Data to practice Data by Zipcode}
colnames(prac)[89] <- "Zip"
#Calling the practice data, with income values added "fin"
fin <- left_join(prac,zip_inc,by="Zip")
#Fix id's to be like original (either read or write csv functions dropped the leading 0s somewhere)
fin$practice_id2 <- str_pad(fin$practice_id2,9,"left","0")
names(prac)
head(fin)
```

```{r Filter Data to Underperforming Measures and Ditch ZERO or NA Denominators}

C12 <- fin %>% filter(measure_ds == "C12: Osteoporosis Management in Women who had a Fracture")
C14 <- fin %>% filter(measure_ds == "C14: Comprehensive Diabetes Care: Medical Attention for Nephropathy")
C15 <- fin %>% filter(measure_ds == "C15: Comprehensive Diabetes Care: HbA1c Control (<=9%)")
C17 <- fin %>% filter(measure_ds == "C17: Disease Modifying Anti-Rheumatic Drug Therapy for Rheumatoid Arthritis")
C20 <- fin %>% filter(measure_ds == "C20: Medication Reconciliation Post-Discharge")
DMD15 <- fin %>% filter(measure_ds == "DMD15: Statin Use in Persons with Diabetes")

#Check for NA Denominator
# length(which(is.na(C12$denominator)))
# length(which(is.na(C14$denominator)))
# length(which(is.na(C15$denominator)))
# length(which(is.na(C17$denominator)))
#C20 is the only one with any NA denominators, comment out next line and rerun to see
C20 <- C20 %>% filter(is.na(denominator) == FALSE)
# length(which(is.na(C20$denominator)))
# length(which(is.na(DMD15$denominator)))
#Fin has na denominators for measures outside these guys above
# length(which(is.na(fin$denominator)))

#Filter out ZERO denominators
C12 <- C12 %>% filter(denominator != 0)
C14 <- C14 %>% filter(denominator != 0) 
C15 <- C15 %>% filter(denominator != 0) 
C17 <- C17 %>% filter(denominator != 0)
C20 <- C20 %>% filter(denominator != 0)
DMD15 <- DMD15 %>% filter(denominator != 0)

# length(which(is.na(C12$compliance)))
# length(which(is.na(C14$compliance)))
# length(which(is.na(C15$compliance)))
# length(which(is.na(C17$compliance)))
# length(which(is.na(C20$compliance)))
# length(which(is.na(DMD15$compliance)))

```

```{r Trim All To Relevant Columns and Rename}

#names(C12)

C12 <- C12[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C12) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C14 <- C14[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C14) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C15 <- C15[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C15) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C17 <- C17[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C17) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

C20 <- C20[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(C20) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")

DMD15 <- DMD15[,c(2,52,102,103,89,104,105,106,11,12,22,5,6,36,13:16,40:43,47,48,85:88,64,65,67,74,75,78,101,3)]
colnames(DMD15) <- c("ID","practice_Name","Lon","Lat","Zip","Med_Household","Mean_Household","Pop_of_Zip","Measure","Weight","Compliance","Denominator","Numerator","Aggregate_Stars","Cut2","Cut3","Cut4","Cut5","Needed2","Needed3","Needed4","Needed5","Needed_Next","Gap_Worth","Address","Address_2","City","State","Program","Entity","Health_System","FreedomBlue","SecurityBlue","WV_FreedomBlue","Stars_Par","practice_Mbr_Count")
```

```{r}
names(DMD15)
names(test1)
hail_mary <- left_join(test1,DMD15,by)
```

```{r Rank Measure-Specific Compliance By City -- yeah}

##DMD15
tib1 <- DMD15 %>% filter(Denominator >= 5) %>% group_by(City) %>% summarise(Num = n()) %>% filter(Num > 2) %>% arrange(Num)
want1 <- tib1$City

test1 <- DMD15 %>% filter(Denominator >= 5 & City %in% want1 == TRUE) %>% group_by(City) %>% select(Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Aggregate_Stars,Address,Needed4,Needed5) %>% arrange(City)
test1

bits1 <- unique(test1$City)

temp1 <- c()
for(i in 1:length(bits1)){
  bit <- test1 %>% filter(City == bits1[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp1 <- append(temp1,new)
}

test1$City.Rank <- temp1 

##C12

tib2 <- C12 %>% filter(Denominator >= 5) %>% group_by(City) %>% summarise(Num = n()) %>% filter(Num > 2) %>% arrange(Num)
want2 <- tib2$City

test2 <- C12 %>% filter(Denominator >= 5 & City %in% want1 == TRUE) %>% group_by(City) %>% select(Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Aggregate_Stars,Address,Needed4,Needed5) %>% arrange(City)
test2

bits2 <- unique(test2$City)

temp2 <- c()
for(i in 1:length(bits2)){
  bit <- test2 %>% filter(City == bits2[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp2 <- append(temp2,new)
}

test2$City.Rank <- temp2
test2

##C14

tib3 <- C14 %>% filter(Denominator >= 5) %>% group_by(City) %>% summarise(Num = n()) %>% filter(Num > 2) %>% arrange(Num)
want3 <- tib3$City

test3 <- C14 %>% filter(Denominator >= 5 & City %in% want1 == TRUE) %>% group_by(City) %>% select(Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Aggregate_Stars,Address,Needed4,Needed5) %>% arrange(City)

bits3 <- unique(test3$City)

temp3 <- c()
for(i in 1:length(bits3)){
  bit <- test3 %>% filter(City == bits3[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp3 <- append(temp3,new)
}

test3$City.Rank <- temp3

##C15

tib4 <- C15 %>% filter(Denominator >= 5) %>% group_by(City) %>% summarise(Num = n()) %>% filter(Num > 2) %>% arrange(Num)
want4 <- tib4$City

test4 <- C15 %>% filter(Denominator >= 5 & City %in% want1 == TRUE) %>% group_by(City) %>% select(Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Aggregate_Stars,Address,Needed4,Needed5) %>% arrange(City)

bits4 <- unique(test4$City)

temp4 <- c()
for(i in 1:length(bits4)){
  bit <- test4 %>% filter(City == bits4[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp4 <- append(temp4,new)
}

test4$City.Rank <- temp4

##C17

tib5 <- C17 %>% filter(Denominator >= 5) %>% group_by(City) %>% summarise(Num = n()) %>% filter(Num > 2) %>% arrange(Num)
want5 <- tib5$City

test5 <- C17 %>% filter(Denominator >= 5 & City %in% want1 == TRUE) %>% group_by(City) %>% select(Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Aggregate_Stars,Address,Needed4,Needed5) %>% arrange(City)

bits5 <- unique(test5$City)

temp5 <- c()
for(i in 1:length(bits5)){
  bit <- test5 %>% filter(City == bits5[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp5 <- append(temp5,new)
}

test5$City.Rank <- temp5

##C20

tib6 <- C20 %>% filter(Denominator >= 5) %>% group_by(City) %>% summarise(Num = n()) %>% filter(Num > 2) %>% arrange(Num)
want6 <- tib6$City

test6 <- C20 %>% filter(Denominator >= 5 & City %in% want1 == TRUE) %>% group_by(City) %>% select(Practice_Name = practice_Name,Compliance,Denominator,Med_Household,Aggregate_Stars,Address,Needed4,Needed5) %>% arrange(City)

bits6 <- unique(test6$City)

temp6 <- c()
for(i in 1:length(bits6)){
  bit <- test6 %>% filter(City == bits6[i])
  new <- rank(-bit$Compliance,ties.method="min")
  temp6 <- append(temp6,new)
}

test6$City.Rank <- temp6
```

```{r}

test1 <- test1[,c(1,2,10,3,6,4,7,8,9,5)]
test2 <- test2[,c(1,2,10,3,6,4,7,8,9,5)]
test3 <- test3[,c(1,2,10,3,6,4,7,8,9,5)]
test4 <- test4[,c(1,2,10,3,6,4,7,8,9,5)]
test5 <- test5[,c(1,2,10,3,6,4,7,8,9,5)]
test6 <- test6[,c(1,2,10,3,6,4,7,8,9,5)]

names(test4)
```

```{r Export to .csv}
write.csv(test2, file="C12Ranked.csv", row.names = FALSE)
write.csv(test3, file="C14Ranked.csv", row.names = FALSE)
write.csv(test4, file="C15Ranked.csv", row.names = FALSE)
write.csv(test5, file="C17Ranked.csv", row.names = FALSE)
write.csv(test6, file="C20Ranked.csv", row.names = FALSE)
write.csv(test1, file="DMD15Ranked.csv", row.names = FALSE)
```

```{r View 'em}
head(C12) 
head(C14)
head(C15)
head(C17)
head(C20)
head(DMD15)
```

```{r Compare Denominators just curious}
#Compare Summed Denominators
cat("\nsum C12 is:",sum(C12$Denominator),"sum C14 is:",sum(C14$Denominator),"sum C15 is:",sum(C15$Denominator),"sum C17 is:",sum(C17$Denominator),"sum C20 is:",sum(C20$Denominator,na.rm =TRUE),"sum DMD15 is:",sum(DMD15$Denominator),"\n")
#Max and Mins
max(C12$Denominator)
min(C12$Denominator)
max(C14$Denominator)
min(C14$Denominator)
max(C15$Denominator)
min(C15$Denominator)
max(C17$Denominator)
min(C17$Denominator)
max(C20$Denominator)
min(C20$Denominator)
max(DMD15$Denominator)
min(DMD15$Denominator)
```

```{r Prep Map}
#xxxxxxx_Your_API_Key_Here_xxxxxxxxxx
register_google(key ="xxxxxxx_Your_API_Key_Here_xxxxxxxxxx")
map <- get_map(location = "State College", zoom = 7, maptype = "roadmap", source = "google", color = "color")
```

```{r C12 Geo Compliance}
#jpeg("2-17-19 C12 Geo Compliance.jpg")
ggmap(map) + geom_point(aes(x = Lon, y = Lat,  colour = Compliance, size=Denominator),data = C12, alpha = 0.7) + xlab("Latitude") + ylab("Longitude") + ggtitle("C12 Compliance by Location")
#dev.off()
```

```{r C14 Geo Compliance}
#jpeg("2-17-19 C14 Geo Compliance.jpg")
ggmap(map) + geom_point(aes(x = Lon, y = Lat,  colour = Compliance, size=Denominator),data = C14, alpha = 0.7) + xlab("Latitude") + ylab("Longitude") + ggtitle("C14 Compliance by Location")
#dev.off()
```

```{r C15 Geo Compliance}
#jpeg("2-17-19 C15 Geo Compliance.jpg")
ggmap(map) + geom_point(aes(x = Lon, y = Lat,  colour = Compliance, size=Denominator),data = C15, alpha = 0.7) + xlab("Latitude") + ylab("Longitude") + ggtitle("C15 Compliance by Location")
#dev.off()
```

```{r C17 Geo Compliance}
#jpeg("2-17-19 C17 Geo Compliance.jpg")
ggmap(map) + geom_point(aes(x = Lon, y = Lat,  colour = Compliance, size=Denominator),data = C17, alpha = 0.7) + xlab("Latitude") + ylab("Longitude") + ggtitle("C17 Compliance by Location")
#dev.off()
```

```{r C20 Geo Compliance}
#jpeg("2-17-19 C20 Geo Compliance.jpg")
ggmap(map) + geom_point(aes(x = Lon, y = Lat,  colour = Compliance, size=Denominator),data = C20, alpha = 0.7) + xlab("Latitude") + ylab("Longitude") + ggtitle("C20 Compliance by Location")
#dev.off()
```

```{r DMD15 Geo Compliance}
#jpeg("2-17-19 DMD15 Geo Compliance.jpg")
ggmap(map) + geom_point(aes(x = Lon, y = Lat,  colour = Compliance, size=Denominator),data = DMD15, alpha = 0.7) + xlab("Latitude") + ylab("Longitude") + ggtitle("DMD15 Compliance by Location")
#dev.off()
```
